Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-16 paper/paper.tex
Add student report as ref
Remove dangling literature
Resort and tweak overview table

@@

\begin{table}[!t]
  \normalsize
  \caption{Software packages of the case study}
  \label{table:label-distribution}
  \centering
  \begin{tabular}{|l|l|l|l|}
    \hline
    \bfseries Package & \bfseries Type & \bfseries Build system & \bfseries Version \\ \hline
    precice & library & cmake & 2.5.0 \\ \hline
    fortran-module & bindings & make & 9e3f405 \\ \hline
    julia & bindings & julia & 2.5.0 \\ \hline
    matlab & bindings & matlab build script & 2.5.0.0 \\ \hline
    pyprecice & bindings & setup.py & 2.5.0.1 \\ \hline
    config-visualizer & tooling & setup.py & 60f2165 \\ \hline
    precice-aste & tooling & cmake & 3.0.0 \\ \hline
    dealii & solver & cmake & 9.4.1 \\ \hline
    precice-dealii-adapter & adapter & cmake & dbb25bea \\ \hline
    precice-calculix-adapter & solver + adapter & makefile & 2.20 \\ \hline
    fenics & solver library& cmake + setup.py & 2019.1.0 \\ \hline
    precice-fenics-adapter & adapter & setup.py & 1.4.0 \\ \hline
    precice-dune & adapter & scripts + cmake & 2.8.0 \\ \hline
    dune-fem & solver library & setup.py & 2.8.0.0 \\ \hline
    code-aster & solver & custom build system in python & 14.6.0 \\ \hline
    openfoam & solver & wmake/Allwmake & 2206 \\ \hline
    openfoam-adapter & adapter & wmake/Allwmake & 1.2.1 \\ \hline
    precice-su2 & solver + adapter & patch script + autoconf & 6.0.0 \\ \hline
    nutils & solver library & setup.py & 7.0.0 \\ \hline
  \end{tabular}
\end{table}

@@

\subsubsection{Fortran bindings}

@@

This paper is the result of a student research project and a streamlined version of its report~\cite{TODO}. Beyond this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

@@

\nocite{*}
\bibliographystyle{eceasst}
\bibliography{paper}

>>>>

This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}.

@@

\begin{table}[!t]
  \normalsize
  \caption{Software packages of the case study}
  \label{table:label-distribution}
  \centering
  \begin{tabular}{|l|l|l|l|}
    \hline
    \bfseries Package & \bfseries Type & \bfseries Build system & \bfseries Version \\ \hline
    preCICE & library & cmake & 2.5.0 \\ \hline
    Fortran module & bindings & make & 9e3f405 \\ \hline
    Julia bindings & bindings & julia & 2.5.0 \\ \hline
    Matlab bindings & bindings & matlab build script & 2.5.0.0 \\ \hline
    Python bindings & bindings & setup.py & 2.5.0.1 \\ \hline
    ASTE & tooling & cmake & 3.0.0 \\ \hline
    Config visualizer & tooling & setup.py & 60f2165 \\ \hline
    preCICE-CalculiX adapter & solver + adapter & makefile & 2.20 \\ \hline
    Code\_Aster & solver & custom system in python & 14.6.0 \\ \hline
    Code\_Aster-preCICE adapter & adapter & custom system in python & ce995e0 \\ \hline
    deal.II & solver & cmake & 9.4.1 \\ \hline
    preCICE-deal.II adapter & adapter & cmake & dbb25bea \\ \hline
    DUNE-FEM & solver library & setup.py & 2.8.0 \\ \hline
    preCICE-DUNE adapter& adapter & scripts + cmake & 5f2364d \\ \hline
    FEniCS & solver library& cmake + setup.py & 2019.1.0 \\ \hline
    preCICE-FEniCS adapter & adapter & setup.py & 1.4.0 \\ \hline
    Nutils & solver library & setup.py & 7.0.0 \\ \hline
    OpenFOAM & solver & wmake/Allwmake & 2206 \\ \hline
    preCICE-OpenFOAM adapter & adapter & wmake/Allwmake & 1.2.1 \\ \hline
    preCICE-SU2 adapter & solver + adapter & patch script + autoconf & 6.0.0 \\ \hline
  \end{tabular}
\end{table}

@@

\subsubsection{Fortran module}

@@

This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}. Beyond this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

@@

\bibliographystyle{eceasst}
\bibliography{paper}
